The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update lcres discussion

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased rapidly between 5 m and 50 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). Layer similarity (Figure \@ref(fig:socres)c) and connective redundancy (Figure \@ref(fig:socres)d) were relatively stable across social thresholds. Taken together, these results suggest the optimal
<!-- TODO: why optimal -->
social scale at which groups should be assigned is likely somewhere between ~20
- 100 m based on the rate at which network metrics stabilized. For ungulates,
groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
2018; Peignier et al. 2019), suggesting that given similar quantities of data,
~50 m is likely an appropriate social scale for generating social networks in
caribou and similar species.
<!-- TODO: missing summer relevance -->

Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m, there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure \@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->

>>>>

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased rapidly between 5 m and 50 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). Layer similarity (Figure \@ref(fig:socres)c) and connective redundancy (Figure \@ref(fig:socres)d) were relatively stable across social thresholds. Taken together, these results suggest the optimal
<!-- TODO: why optimal -->
social scale at which groups should be assigned is likely somewhere between ~20
- 100 m based on the rate at which network metrics stabilized. For ungulates,
groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
2018; Peignier et al. 2019), suggesting that given similar quantities of data,
~50 m is likely an appropriate social scale for generating social networks in
caribou and similar species.
<!-- TODO: missing summer relevance .. the actual value of layer sim?-->

(ref:lcres) Varying spatial scale in landcover resolution. For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength of individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m. Individuals in summer layers had consistent weak connections. B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) was relatively stable for forest and open, except for a sharp decrease in open at 100 m and 250 m. Note that layer similarity in summer forage is not shown because individuals did not interact at landcover resolutions greater than 30 m and therefore layer similarity could not be calculated. D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in these habitats. Mean graph strength increased consistently in winter forest and open habitats. Mean graph strength in winter forage <!-- TODO: check this fig A/C similar lines--> Individuals in summer layers had consistent weak connections. Layer relevance was stable in winter for open and forest habitats but decreased for forage habitats (Figure \@ref(fig:lcres)b). Layer relevance was stable for all habitat classes in summer layers. Layer similarity was stable for forest and open, except for a sharp decrease in layer similarity in open at 100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m, there were no individuals connected in the network
layers. Individuals still used forage habitats but given a lower availability due to increasing landcover resolution, at a much lower rate. Connective redundancy slightly decreased as landcover resolution increased (Figure \@ref(fig:lcres)d). These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect landscape features and habitats relevant to study species. 
<!-- TODO: how? This isn't clear enough for me to follow yet -->
